---
title: "All_experiments_AttackAffordance"
author: "Song Qi"
date: '2022-07-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and packages

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)

exp_all <- read.csv("~/Downloads/exp_all_AttackAffordance.csv")
```

## Number of subjects
```{r}
length(unique(exp_all$subject))

```

## Number of stimulus
```{r}
length(unique(exp_all$type2))

```

## Categorical presentation of choice by contingency

```{r}
cross_tab_choice_contingency <-table(exp_all$contingency,exp_all$choice)
prop_choice_contingency <- data.frame(prop.table(cross_tab_choice_contingency,1)*100)
colnames(prop_choice_contingency) <- c("contingency", "choice", "percentage")
prop_choice_contingency$contingency <- factor(prop_choice_contingency$contingency)
prop_choice_contingency_chisq <- chisq.test(exp_all$contingency,exp_all$choice)
prop_choice_contingency_chisq_stats <- round(with(prop_choice_contingency_chisq, c(statistic, parameter, p.value)), 3)

prop_choice_contingency$counts <- c(cross_tab_choice_contingency[1,1], cross_tab_choice_contingency[2,1],cross_tab_choice_contingency[1,2],    cross_tab_choice_contingency[2,2])

prop_choice_contingency

```


##Graph categorical presentation of choice and contingency
```{r}
prop_choice_contingency %>%
   ggplot(aes(x = contingency, y = percentage, fill = choice)) +
   geom_bar(stat="identity", position=position_dodge(.93)) +
   ggtitle("choice by contingency") +
   ylab("percentage chosen") +
annotate("text", x = 1, y = 75, label = paste0("χ2 = ", prop_choice_contingency_chisq_stats[1], ", df = ", prop_choice_contingency_chisq_stats[2], ", p = ", prop_choice_contingency_chisq_stats[3] ))


```



## Check distribution of anger and fear 
```{r}
hist(exp_all$anger_rating)
hist(exp_all$fear_rating)
```



## Look at average levels of anger by contingency
```{r}
levels_contingency <- levels(as.factor(exp_all$contingency)) 
avg_anger_rating <- 0
sd_anger_rating <- 0
for (i in seq(levels_contingency)){
  avg_anger_rating[i] <- mean(exp_all[exp_all$contingency==levels_contingency[i],]$anger_rating)
  sd_anger_rating[i] <-  sd(exp_all[exp_all$contingency==levels_contingency[i],]$anger_rating)
  avg_anger_ratings_by_contingency <- data.frame(cbind(levels_contingency,avg_anger_rating,sd_anger_rating ))
}
avg_anger_ratings_by_contingency

```

## Plot the anger mean differences between contingencies and t-test results
```{r}
test_mean_anger <- t.test(exp_all$anger_rating ~ exp_all$contingency, paired = TRUE)

exp_all %>%
  ggplot(aes(x = contingency, y = anger_rating)) +
  geom_boxplot() +
  annotate("text", x = 1.5, y = 5.5, label = paste0("t = ", round(test_mean_anger$statistic[1],2), ", df = ,", test_mean_anger$parameter, "\n", "p = ", test_mean_anger$p.value ))


```

## Plot the anger mean differences between contingencies broken down by choice

```{r}

exp_all %>%
  ggplot(aes(x = contingency, y = anger_rating)) +
  geom_boxplot() +
  facet_grid(~choice)


aov_test <- aov(anger_rating ~ contingency2 * choice2, data = exp_all)
summary(aov_test)

```




## positive slopes for each subject

```{r}
slopes <- matrix(NA, nrow = length(unique(exp_all$subject)),ncol=length(unique(exp_all$type2)))

for (j in seq(unique(exp_all$subject))){
  for (i in seq(unique(exp_all$type2))) {
    
    slopes[j,i] <- exp_all[exp_all$contingency=="weapon" & exp_all$type2 == i & exp_all$subject == j,]$anger_rating - exp_all[exp_all$contingency=="non_weapon" & exp_all$type2 == i & exp_all$subject == j ,]$anger_rating
    
    anger_slopes_df <- data.frame(cbind(subect = unique(exp_all$subject), slopes))
    colnames(anger_slopes_df) <- c("subject", unique(exp_all$type2))
  }
}

```


## proportion of positive slopes
```{r}

proportion_pos_slopes_per_subject <- 0 

for (i in seq(nrow(anger_slopes_df))){
  proportion_pos_slopes_per_subject[i] <-
    sum(anger_slopes_df[i,c(2:21)]>0)/length(anger_slopes_df[i,c(2:21)])
}

proportion_pos_slopes_per_subject

average_positive_slopes_across_subjects <- mean(proportion_pos_slopes_per_subject)
paste0 ("average_positive_slopes_across_subjects = ", print(average_positive_slopes_across_subjects))



```

## proportion of positive slopes (only fighting)
```{r}
slopes_weapon <- matrix(NA, nrow =  length(unique(exp_all$subject)), ncol = length(unique(exp_all$type2)) )

for (j in seq(unique(exp_all$subject))){ 
  for (i in seq(unique(exp_all$type2))) {
    
    slopes_weapon[j,i] <- exp_all[exp_all$contingency=="weapon" & exp_all$type2 == i & exp_all$subject == j ,]$choice
    
  } }



positive_slopes_when_weapon_and_fight <- anger_slopes_df[slopes_weapon == "fight", ]
positive_slopes_when_weapon_and_esccape <- anger_slopes_df[slopes_weapon == "escape", ]



proportion_pos_slopes_per_subject_fight <- 0
for (i in seq(nrow(positive_slopes_when_weapon_and_fight)))
{
  proportion_pos_slopes_per_subject_fight[i] <-
    sum(positive_slopes_when_weapon_and_fight[i,c(2:21)]>0)/length(positive_slopes_when_weapon_and_fight[i,c(2:21)])
}



average_positive_slopes_across_subjects_fight <- mean(proportion_pos_slopes_per_subject_fight, na.rm = TRUE)

paste0 ("average_positive_slopes_across_subjects_fight =",print(average_positive_slopes_across_subjects_fight))


```



## proportion of positive slopes (add labels)
```{r}

store_slope <- data.frame(slope = 0,subject = 0,stim = 0,label = 0)


for (j in 1:572){
  for (k in 1:20){
    
    slope = exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == 1,]$anger_rating - exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == -1,]$anger_rating
    
    subject = j
    stim = k
    
    if (exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == 1,]$choice2 == "1" & exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == -1,]$choice2 == "1") {label = "F-F"}
    
    else if (exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == 1,]$choice2 == "1" & exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == -1,]$choice2 == "-1") {label = "F-E"}
    
    else if (exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == 1,]$choice2 == "-1" & exp_all[exp_all$subject == j & exp_all$type2 == k & exp_all$contingency2 == -1,]$choice2 == "-1") {label = "E-E"}
    
    else {label = "E-F"}
    
    temp = data.frame(slope = slope, subject = subject, stim = stim, label = label)
    store_slope = rbind(store_slope,temp)
    
  }}

store_slope <- store_slope[-1,]

test1 <- filter(store_slope,label == "F-F")
test2 <- filter(store_slope,label == "F-E")
test3 <- filter(store_slope,label == "E-E")
test4 <- filter(store_slope,label == "E-F")

length(test1[test1$slope>0,]$slope)/length(test1$slope)
length(test2[test2$slope>0,]$slope)/length(test2$slope)
length(test3[test3$slope>0,]$slope)/length(test3$slope)
length(test4[test4$slope>0,]$slope)/length(test4$slope)




store_slope$subject <- as.factor(store_slope$subject)
store_slope$stim <- as.factor(store_slope$stim)


store_slope %>%
  ggplot(aes(x = label, y = slope, fill = stim)) +
  geom_bar(stat="identity", position=position_dodge(.93)) +
  ggtitle("slope by label and stim") +
  ylab("slope") +
  annotate("text", x = 3, y = 7.5, label = paste0("F-F = ", length(test1$slope), ", F-E = ", length(test2$slope), 
                                                  ", E-E = ", length(test3$slope), ", E-F = ", length(test4$slope) ))



store_slope %>%
  ggplot(aes(x = label, y = slope, fill = subject)) +
  geom_bar(stat="identity", position=position_dodge(.93)) +
  ggtitle("slope by label and subject") +
  ylab("slope") +
  annotate("text", x = 3, y = 7.5, label = paste0("F-F = ", length(test1$slope), ", F-E = ", length(test2$slope), 
                                                  ", E-E = ", length(test3$slope), ", E-F = ", length(test4$slope) ))



```




## Print out positive slope percentage, and positive slope magnitude. 
```{r}
length(test1[test1$slope>0,]$slope)/length(test1$slope)
length(test2[test2$slope>0,]$slope)/length(test2$slope)
length(test3[test3$slope>0,]$slope)/length(test3$slope)
length(test4[test4$slope>0,]$slope)/length(test4$slope)

mean(test1[test1$slope>0,]$slope)
mean(test2[test2$slope>0,]$slope)
mean(test3[test3$slope>0,]$slope)
mean(test4[test4$slope>0,]$slope)

p<-ggplot(store_slope, aes(x=slope, color=label)) +
  geom_histogram(fill="white", position="dodge",binwidth = 0.1)+
  #geom_density(alpha=0.6) + 
  theme(legend.position="top")

p

store_slope1 <- data.frame(store_slope,experiment = "1")
```

## Bayesian models, Bayes factors and Loo-comparisons
```{r}
# Bridge sampling
prior_mixed = get_prior(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                        data   = exp_all)


prior_mixed_2 = get_prior(anger_rating ~ contingency2 + choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2 ),
                        data   = exp_all)

full_brms = brm(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                data   = exp_all,prior = prior_mixed,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

null_brms = update(full_brms, formula = ~ .-contingency2:choice2)


null_brms = brm(anger_rating ~ contingency2 + choice2  + (contingency2 + choice2 |subject)  + (contingency2 + choice2|type2),
                data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

test_trst <- full_brms

BF_brms_bridge = bayes_factor(full_brms, test_trst)

BF_brms_bridge


# Bayes_factor package

full_BF = lmBF(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + subject + type2,
               data   = exp_all,whichRandom = "type2")

null_BF = lmBF(anger_rating ~ contingency2 + choice2 + subject + type2,
               data   = exp_all,whichRandom = "type2")

              #data   = exp_all,whichRandom = c("subject","type2"))

full_BF/null_BF


# BIC

BF_BIC = exp((BIC(null_brms) - BIC(full_brms))/2)


# try re-scaling the prior

newprior.bf = generalTestBF(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + subject,
                      data   = exp_all,whichRandom = c("subject"))

newprior.bf 




# new test null 

null_brms = brm(anger_rating ~ contingency2 + choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

BF_brms_bridge = bayes_factor(full_brms, null_brms)

BF_brms_bridge

####

prior_mixed_2 = get_prior(anger_rating ~ choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2 ),
                          data   = exp_all)


null_brms2 <- brm(anger_rating ~ choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                  data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

BF_brms_bridge = bayes_factor(full_brms, null_brms2)

####
loo_compare

fit1 <- add_criterion(full_brms, "waic")
fit2 <- add_criterion(null_brms, "waic")


loo_compare(fit1,fit2,criterion = "waic")

fit3 <- add_criterion(null_brms2, "waic")


loo_compare(fit1,fit3,criterion = "waic")


## more regular statistics

summary(full_brms)

plot(full_brms)

pp = brms::pp_check(full_brms)
pp + theme_bw()
```




