---
title: "Experiment1"
author: "Song Qi"
date: "1/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and packages

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
Experiment1 <- read.csv("~/Downloads/ex1.csv")
```

## Number of subjects
```{r}
length(unique(Experiment1$subject))

```


## Number of stimulus
```{r}
length(unique(Experiment1$type2))

```

## Create new contingency and choice variables with labels
```{r}
Experiment1$contingency <- ifelse(Experiment1$contingency2 == 1, "weapon", "non_weapon")

Experiment1$choice <- ifelse(Experiment1$choice2 == 1, "fight", "escape")

```
## Categorical presentation of choice by contingency

```{r}

cross_tab_choice_contingency <-table(Experiment1$contingency,Experiment1$choice)
 prop_choice_contingency <- data.frame(prop.table(cross_tab_choice_contingency,1)*100)
 colnames(prop_choice_contingency) <- c("contingency", "choice", "percentage")
 prop_choice_contingency$contingency <- factor(prop_choice_contingency$contingency)
 prop_choice_contingency_chisq <- chisq.test(Experiment1$contingency,Experiment1$choice)
 prop_choice_contingency_chisq_stats <- round(with(prop_choice_contingency_chisq, c(statistic, parameter, p.value)), 3)
 
 prop_choice_contingency$counts <- c(cross_tab_choice_contingency[1,1], cross_tab_choice_contingency[2,1],cross_tab_choice_contingency[1,2],    cross_tab_choice_contingency[2,2])
 
 prop_choice_contingency

```


##Graph categorical presentation of choice and contingency
```{r}

prop_choice_contingency %>%
   ggplot(aes(x = contingency, y = percentage, fill = choice)) +
   geom_bar(stat="identity", position=position_dodge(.93)) +
   ggtitle("choice by contingency") +
   ylab("percentage chosen") +
annotate("text", x = 1, y = 75, label = paste0("χ2 = ", prop_choice_contingency_chisq_stats[1], ", df = ", prop_choice_contingency_chisq_stats[2], ", p = ", prop_choice_contingency_chisq_stats[3] ))
```

## Check distribution of anger and fear 
```{r}
 hist(Experiment1$anger_rating)
 hist(Experiment1$fear_rating)
```

## Look at average levels of anger by contingency

```{r}
levels_contingency <- levels(as.factor(Experiment1$contingency)) 
avg_anger_rating <- 0
sd_anger_rating <- 0
for (i in seq(levels_contingency)){
   avg_anger_rating[i] <- mean(Experiment1[Experiment1$contingency==levels_contingency[i],]$anger_rating)
   sd_anger_rating[i] <-  sd(Experiment1[Experiment1$contingency==levels_contingency[i],]$anger_rating)
 avg_anger_ratings_by_contingency <- data.frame(cbind(levels_contingency,avg_anger_rating,sd_anger_rating ))
 }
 avg_anger_ratings_by_contingency
```

## Plot the anger mean differences between contingencies and t-test results

```{r}
test_mean_anger <- t.test(Experiment1$anger_rating ~ Experiment1$contingency, paired = TRUE)

 Experiment1 %>%
   ggplot(aes(x = contingency, y = anger_rating)) +
   geom_boxplot() +
   annotate("text", x = 1.5, y = 5.5, label = paste0("t = ", round(test_mean_anger$statistic[1],2), ", df = ,", test_mean_anger$parameter, "\n", "p = ", test_mean_anger$p.value ))
```

## Plot the anger mean differences between contingencies broken down by choice

```{r}
Experiment1 %>%
   ggplot(aes(x = contingency, y = anger_rating)) +
   geom_boxplot() +
   facet_grid(~choice)


aov_test <- aov(anger_rating ~ contingency2 * choice2, data = Experiment1)
summary(aov_test)

```

## positive slopes for each subject

```{r}

slopes <- matrix(NA, nrow = length(unique(Experiment1$subject)),ncol=length(unique(Experiment1$type2)))

for (j in seq(unique(Experiment1$subject))){
for (i in seq(unique(Experiment1$type2))) {
  
slopes[j,i] <- Experiment1[Experiment1$contingency=="weapon" & Experiment1$type2 == i & Experiment1$subject == j,]$anger_rating - Experiment1[Experiment1$contingency=="non_weapon" & Experiment1$type2 == i & Experiment1$subject == j ,]$anger_rating

 anger_slopes_df <- data.frame(cbind(subect = unique(Experiment1$subject), slopes))
  colnames(anger_slopes_df) <- c("subject", unique(Experiment1$type2))
 }
 }

```

## proportion of positive slopes
```{r}
proportion_pos_slopes_per_subject <- 0 
for (i in seq(nrow(anger_slopes_df))){
   proportion_pos_slopes_per_subject[i] <-
     sum(anger_slopes_df[i,c(2:28)]>0)/length(anger_slopes_df[i,c(2:28)])
 }
 proportion_pos_slopes_per_subject
 
 average_positive_slopes_across_subjects <- mean(proportion_pos_slopes_per_subject)
 paste0 ("average_positive_slopes_across_subjects = ", print(average_positive_slopes_across_subjects))
 
 
```

## proportion of positive slopes (only fighting)

```{r}
slopes_weapon <- matrix(NA, nrow =  length(unique(Experiment1$subject)), ncol = length(unique(Experiment1$type2)) )

for (j in seq(unique(Experiment1$subject))){ 
  for (i in seq(unique(Experiment1$type2))) {
    
slopes_weapon[j,i] <- Experiment1[Experiment1$contingency=="weapon" & Experiment1$type2 == i & Experiment1$subject == j ,]$choice

} }



positive_slopes_when_weapon_and_fight <- anger_slopes_df[slopes_weapon == "fight", ]
positive_slopes_when_weapon_and_esccape <- anger_slopes_df[slopes_weapon == "escape", ]



proportion_pos_slopes_per_subject_fight <- 0
for (i in seq(nrow(positive_slopes_when_weapon_and_fight)))
  {
   proportion_pos_slopes_per_subject_fight[i] <-
  sum(positive_slopes_when_weapon_and_fight[i,c(2:28)]>0)/length(positive_slopes_when_weapon_and_fight[i,c(2:28)])
}



average_positive_slopes_across_subjects_fight <- mean(proportion_pos_slopes_per_subject_fight, na.rm = TRUE)
 
paste0 ("average_positive_slopes_across_subjects_fight =",print(average_positive_slopes_across_subjects_fight))

```

## proportion of positive slopes (add labels)

```{r}

store_slope <- data.frame(slope = 0,subject = 0,stim = 0,label = 0)


  for (j in 1:80){
    for (k in 1:27){
      
      slope = Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == 1,]$anger_rating - Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == -1,]$anger_rating
      
      subject = j
      stim = k
      
      if (Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == 1,]$choice2 == "1" & Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == -1,]$choice2 == "1") {label = "F-F"}
      
      else if (Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == 1,]$choice2 == "1" & Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == -1,]$choice2 == "-1") {label = "F-E"}
      
       else if (Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == 1,]$choice2 == "-1" & Experiment1[Experiment1$subject == j & Experiment1$type2 == k & Experiment1$contingency2 == -1,]$choice2 == "-1") {label = "E-E"}
      
       else {label = "E-F"}
      
      temp = data.frame(slope = slope, subject = subject, stim = stim, label = label)
      store_slope = rbind(store_slope,temp)
  
    }}

store_slope <- store_slope[-1,]

test1 <- filter(store_slope,label == "F-F")
test2 <- filter(store_slope,label == "F-E")
test3 <- filter(store_slope,label == "E-E")
test4 <- filter(store_slope,label == "E-F")

length(test1[test1$slope>0,]$slope)/length(test1$slope)
length(test2[test2$slope>0,]$slope)/length(test2$slope)
length(test3[test3$slope>0,]$slope)/length(test3$slope)
length(test4[test4$slope>0,]$slope)/length(test4$slope)




store_slope$subject <- as.factor(store_slope$subject)
store_slope$stim <- as.factor(store_slope$stim)


store_slope %>%
  ggplot(aes(x = label, y = slope, fill = stim)) +
  geom_bar(stat="identity", position=position_dodge(.93)) +
  ggtitle("slope by label and stim") +
  ylab("slope") +
  annotate("text", x = 3, y = 7.5, label = paste0("F-F = ", length(test1$slope), ", F-E = ", length(test2$slope), 
                                                 ", E-E = ", length(test3$slope), ", E-F = ", length(test4$slope) ))



store_slope %>%
  ggplot(aes(x = label, y = slope, fill = subject)) +
  geom_bar(stat="identity", position=position_dodge(.93)) +
  ggtitle("slope by label and subject") +
  ylab("slope") +
  annotate("text", x = 3, y = 7.5, label = paste0("F-F = ", length(test1$slope), ", F-E = ", length(test2$slope), 
                                                  ", E-E = ", length(test3$slope), ", E-F = ", length(test4$slope) ))




```


## Print out positive slope percentage, and positive slope magnitude. 

```{r}
length(test1[test1$slope>0,]$slope)/length(test1$slope)
length(test2[test2$slope>0,]$slope)/length(test2$slope)
length(test3[test3$slope>0,]$slope)/length(test3$slope)
length(test4[test4$slope>0,]$slope)/length(test4$slope)

mean(test1[test1$slope>0,]$slope)
mean(test2[test2$slope>0,]$slope)
mean(test3[test3$slope>0,]$slope)
mean(test4[test4$slope>0,]$slope)

p<-ggplot(store_slope, aes(x=slope, color=label)) +
  geom_histogram(fill="white", position="dodge",binwidth = 0.1)+
  #geom_density(alpha=0.6) + 
  theme(legend.position="top")

p

store_slope1 <- data.frame(store_slope,experiment = "1")


```



