---
title: "Full_Affordance1"
author: "Song Qi"
date: '2022-07-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and packages

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)

escape1 <- read.csv("~/Downloads/exp1_Full_Affordance.csv")
```

## Number of subjects
```{r}
length(unique(escape1$subject))

```

## Number of stimulus
```{r}
length(unique(escape1$type2))

```

## Categorical presentation of choice by contingency

```{r}
cross_tab_choice_contingency <-table(escape1$Affordance,escape1$choice)

prop_choice_contingency <- data.frame(prop.table(cross_tab_choice_contingency,1)*100)

colnames(prop_choice_contingency) <- c("Affordance", "choice", "percentage")

prop_choice_contingency$contingency <- factor(prop_choice_contingency$Affordance)

prop_choice_contingency_chisq <- chisq.test(escape1$Affordance,escape1$choice)

prop_choice_contingency_chisq_stats <- round(with(prop_choice_contingency_chisq, c(statistic, parameter, p.value)), 3)

prop_choice_contingency$counts <- c(cross_tab_choice_contingency[1,1], cross_tab_choice_contingency[2,1],cross_tab_choice_contingency[1,2],    cross_tab_choice_contingency[2,2])

prop_choice_contingency

```


##Graph categorical presentation of choice and contingency
```{r}
prop_choice_contingency %>%
  ggplot(aes(x = Affordance, y = percentage, fill = choice)) +
  geom_bar(stat="identity", position=position_dodge(.93)) +
  ggtitle("choice by Affordance") +
  ylab("percentage chosen") +
  annotate("text", x = 1, y = 75, label = paste0("χ2 = ", prop_choice_contingency_chisq_stats[1], ", df = ", prop_choice_contingency_chisq_stats[2], ", p = ", prop_choice_contingency_chisq_stats[3] ))


```



## Check distribution of anger and fear 
```{r}
hist(escape1$anger_rating)
hist(escape1$fear_rating)
```



## Look at average levels of anger by contingency
```{r}
levels_contingency <- levels(as.factor(escape1$Affordance)) 
avg_anger_rating <- 0
sd_anger_rating <- 0

for (i in seq(levels_contingency)){
  avg_anger_rating[i] <- mean(escape1[escape1$Affordance==levels_contingency[i],]$anger_rating)
  sd_anger_rating[i] <-  sd(escape1[escape1$Affordance==levels_contingency[i],]$anger_rating)
  avg_anger_ratings_by_contingency <- data.frame(cbind(levels_contingency,avg_anger_rating,sd_anger_rating ))
}

avg_anger_ratings_by_contingency


```

## Plot the anger mean differences between contingencies and t-test results
```{r}
test_mean_anger <- t.test(escape1$anger_rating ~ escape1$contingency2, paired = TRUE)

escape1 %>%
  ggplot(aes(x = contingency2, y = anger_rating)) +
  geom_boxplot() +
  annotate("text", x = 1.5, y = 5.5, label = paste0("t = ", round(test_mean_anger$statistic[1],2), ", df = ,", test_mean_anger$parameter, "\n", "p = ", test_mean_anger$p.value ))


```

## Plot the anger mean differences between contingencies broken down by choice

```{r}

escape1 %>%
  ggplot(aes(x = Affordance, y = anger_rating)) +
  geom_boxplot() +
  facet_grid(~choice)

escape1 %>%
  ggplot(aes(x = Affordance, y = fear_rating)) +
  geom_boxplot() +
  facet_grid(~choice)


aov_test <- aov(anger_rating ~ Affordance * choice, data = escape1)
summary(aov_test)

aov_test <- aov(fear_rating ~ Affordance * choice, data = escape1)
summary(aov_test)

```



## Bayesian models, Bayes factors and Loo-comparisons
```{r}
# Bridge sampling
prior_mixed = get_prior(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                        data   = exp_all)


prior_mixed_2 = get_prior(anger_rating ~ contingency2 + choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2 ),
                        data   = exp_all)

full_brms = brm(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                data   = exp_all,prior = prior_mixed,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

null_brms = update(full_brms, formula = ~ .-contingency2:choice2)


null_brms = brm(anger_rating ~ contingency2 + choice2  + (contingency2 + choice2 |subject)  + (contingency2 + choice2|type2),
                data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

test_trst <- full_brms

BF_brms_bridge = bayes_factor(full_brms, test_trst)

BF_brms_bridge


# Bayes_factor package

full_BF = lmBF(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + subject + type2,
               data   = exp_all,whichRandom = "type2")

null_BF = lmBF(anger_rating ~ contingency2 + choice2 + subject + type2,
               data   = exp_all,whichRandom = "type2")

              #data   = exp_all,whichRandom = c("subject","type2"))

full_BF/null_BF


# BIC

BF_BIC = exp((BIC(null_brms) - BIC(full_brms))/2)


# try re-scaling the prior

newprior.bf = generalTestBF(anger_rating ~ contingency2 + choice2 + contingency2:choice2 + subject,
                      data   = exp_all,whichRandom = c("subject"))

newprior.bf 




# new test null 

null_brms = brm(anger_rating ~ contingency2 + choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

BF_brms_bridge = bayes_factor(full_brms, null_brms)

BF_brms_bridge

####

prior_mixed_2 = get_prior(anger_rating ~ choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2 ),
                          data   = exp_all)


null_brms2 <- brm(anger_rating ~ choice2 + (contingency2 + choice2 + contingency2:choice2|subject)  + (contingency2 + choice2 + contingency2:choice2|type2),
                  data   = exp_all,prior = prior_mixed_2,sample_prior = TRUE,save_pars = save_pars(all = TRUE),iter = 10000,control = list(adapt_delta = 0.99))

BF_brms_bridge = bayes_factor(full_brms, null_brms2)

####
loo_compare

fit1 <- add_criterion(full_brms, "waic")
fit2 <- add_criterion(null_brms, "waic")


loo_compare(fit1,fit2,criterion = "waic")

fit3 <- add_criterion(null_brms2, "waic")


loo_compare(fit1,fit3,criterion = "waic")


## more regular statistics

summary(full_brms)

plot(full_brms)

pp = brms::pp_check(full_brms)
pp + theme_bw()
```




